Generating Images From Captions\\ With Attention

### 2015-10-07 figures/iclr-paper.tex
merged jimmys and elmans changes

\documentclass{article} % For LaTeX2e
\usepackage{iclr-style/iclr2016_conference,times}
\usepackage{hyperref}
\usepackage{url}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{graphicx}
\usepackage{caption}
%\usepackage{subcaption}
\usepackage{subfig}

\newcommand{\comm}[1]{}
\newcommand{\given}{\,|\,}
\newcommand{\expectation}{\mathbb{E}}
\newcommand{\kldiv}{\mathrm{D}_{\rm KL}}
\newcommand{\klBars}{\,\|\,}
\newcommand{\sigmoid}{\boldsymbol{\sigma}}
\newcommand{\hlang}{h^{lang}}
\newcommand{\hlangall}{\boldsymbol{h^{lang}}}
\newcommand{\hdec}{h^{dec}}
\newcommand{\henc}{h^{enc}}
\newcommand{\readop}{\mathit{read}}
\newcommand{\writeop}{\mathit{write}}
\newcommand{\encoder}{\mathit{LSTM}^{enc}}
\newcommand{\decoder}{\mathit{LSTM}^{dec}}
\newcommand{\canv}{c}
\newcommand{\lat}{z}
\newcommand{\Lat}{Z}
\newcommand{\numSamples}{L}
\newcommand{\sampleIdx}{l}
\newcommand{\LatSample}{\tilde{Z}}
\newcommand{\icaption}{{\bf{y}}}
\newcommand{\oimage}{{\bf{x}}}
\newcommand{\post}{Q}
\newcommand{\prior}{P}
\newcommand{\loss}{\mathcal{L}}
\newcommand{\lloss}{\mathcal{L}^{z}}
\newcommand{\rloss}{\mathcal{L}^{x}}

@@

Statistical natural image modelling remains a fundamental problem in computer vision and image understanding. This has motivated recent approaches in generative modelling applied to natural images by employing deep neural networks for their inference and generative components. Image generative models studied previously are often restricted to learning unconditional models of images distribution or conditioned on simple structured annotations, for example classification labels. Despite the advances in generative models, learning the highly structured natural image distribution alone in the high dimensional pixel space alone proves to be a difficult task. In real world, however, images rarely appear in isolation. They often accompanied by their unstructured textual descriptions on web pages and in books. One domain presents substantial amount of relating information of the other domain. The additional information from image and unstructured text description could be used to simplify the image modelling task.

There are two directions in learning a generative model of image and text.  One approach is to learn a text generative model conditioned on the images. Significant amount of recent works have been focusing on generating captions from images\citep{karpathy_captions}, \citep{xu_captions}, \citep{kiros_captions} and etc. The models take an image descriptor and generate unstructured texts through a recurrent decoder. By contrast, learning a generative model for image and text may also be studied by generating images correctly interpreting the text description. 
Generating high dimensional realistic images from their descriptions is a more difficult approach that combines two challenging components of language modelling and image generation. Namely, the model has to capture the semantic meaning expressed in the description and then use that knowledge to generate pixel intensities of the image. Although, the interesting high dimensional natural images lay on a small manifold that is difficult to capture, the additional text description cues of a target image may simplify the learning problem by focusing on the conditional distribution.

In this paper, we illustrate how simple sequential deep learning techniques can be used to build a conditional probabilistic model over natural image space effectively. By using a sequence to sequence framework to approach the problem of image generation from unstructured natural language captions, our model iteratively draws the patches on canvas, while attending to the relevant words in the description. Overall, the main contributions of this work are the following:

@@

Deep Neural Networks have achieved a remarkable performance in various tasks such as image recognition \citep{krizhevsky_imagenet}, speech transcription \citep{graves_speech} and etc. While most of the recent success has been achieved by discriminative models, the generative models have not yet enjoyed the same level of success. Most of the previous work in generative models has been focused on variants of Boltzmann Machines \citep{smolensky_rbm}, \citep{russ_dbm} and Deep Belief Networks \citep{hinton_dbn}. While these models are very powerful, each iteration of training requires a computationally costly step of MCMC to approximate an intractable normalization constant that makes it hard to scale them to large datasets.

@@

\section{Model}
Our proposed model can be viewed as a part of sequence-to-sequence framework \citep{ilya_mt}, \citep{cho_mt}, \citep{nitish_video} where captions are represented as a sequence of consecutive words and images are represented as a sequence of patches drawn on canvas over time $t=1,...,T$. Let $\icaption$ be the input caption, consisting of $N$ words $y_{1}, y_{2}, ..., y_{n}$ and $\oimage$ be the image corresponding to that caption.

\subsection{Language Model: the Bidirectional Attention RNN}
\label{sec:lang}
The input caption sentences are fed into a deterministic Bidirectional LSTM\cite{} that encodes the variable size sentences into the vector representation $s$. Bidirectional LSTM consists of one Forward LSTM and Backward LSTM which combine information from past and future respectively. The Forward LSTM computes the sequence of forward hidden states $[\overrightarrow{h}^{lang}_{1}, \overrightarrow{h}^{lang}_{2}, ..., \overrightarrow{h}^{lang}_{N}]$ , whereas the Backward LSTM computes the sequence of backward hidden states $[\overleftarrow{h}^{lang}_{1}, \overleftarrow{h}^{lang}_{2}, ..., \overleftarrow{h}^{lang}_{N}]$. Then these hidden states are concatenated together into the sequence $[\hlang_{1}, \hlang_{2}, ..., \hlang_{N}]$, where $\hlang_{n} = [\overrightarrow{h}^{lang}_{n}, \overleftarrow{h}^{lang}_{n}], 1\leq n\leq N$.

\subsection{Image Model: the Conditional DRAW Network}

The DRAW network \cite{gregor_draw} is a sequential probabilistic model generating images by accumulating the output at each iterative step. While the original DRAW network assumes the latent variables are independent, it has shown in \citep{bachman_sdm} the model performance is improved by including the dependencies of latent variables.

We extended the architecture the DRAW network generative process to include additional input caption from the language model described in Sec. (\ref{sec:lang}). Similarly to the original DRAW network, the conditional DRAW network is a stochastic recurrent neural network that consists of Inference LSTM that infers the distribution of latent variables of image $x$ given $y$ and then the Generator LSTM that uses the inferred latent variables in order to reconstruct the image $x$ given $y$. The $align$ function is used to compute the alignment between the input caption and intermediate image generative steps as in \cite{bahdanau_mt}:

Formally, the image is generated by iteratively computing the following equations for $t=1,...,T$
\begin{align}
\label{eq:x_hat}
\hat{x}_t &= x-\sigmoid(\canv_{t-1})\\
\label{eq:read}
r_t &= \readop(x_t, \hat{x}_t, \hdec_{t-1})\\
\henc_t &= \encoder(\henc_{t-1}, [r_t, \hdec_{t-1}])\\
\lat_t &\sim \post(\Lat_t|\henc_t)\\
\hdec_t &= \decoder(\hdec_{t-1}, z_t, s_{t-1})\\
s_{t} &= align(\hdec_{t-1}, \hlangall) \\
\label{eq:write}
\canv_t &= \canv_{t-1} + \writeop(\hdec_t)
\end{align}

where $\readop$ and $\writeop$ are the same attention operators as in \citep{gregor_draw}.
Given the caption representation from the language model, $\hlangall = [\hlang_{1}, \hlang_{2}, ..., \hlang_{N}]$, the $algin$ operator computes the final sentence representation $s_t$ through a weighted sum using alignment probabilities $\alpha_{1...N}$:
\begin{align}
s_t=align(\hdec_{t-1}, \hlangall) = \alpha_{1}\hlang_{1} + \alpha_{2}\hlang_{2} + ... + \alpha_{N}\hlang_{N}.
\end{align}

The corresponding alignment probabilities $\alpha_{1...n}$ at each step are obtained by:
\begin{align}
e_{tj} &= v^{T}tanh(U\hlang_{j} + W\hdec_{t} + b)\\
\alpha_{j} &= \frac{exp(e_{tj})}{\sum_{j=1}^{N}exp(e_{tj})}.
\end{align}

Here $\hlang_{0}$ is initialized to the learned bias.
Setting $\alpha_{1...N}$ to $\frac{1}{N}$ turns the encoder into the vanilla model introduced in \citep{cho_mt} without the attention.

@@

The latent loss $\lloss$ is a negative sum of Kullback--Leibler divergence terms between distribution $\post(\Lat_t|\henc_t)$ and some prior distribution ${\prior(\Lat_t)}$ over time $t=1,...,T$, which can be seen as a regularization term. Since the patches drawn on canvas over time are not independent of each other, naturally the sufficient statistics of the prior distribution at time $t$ should be dependent on the sufficient statistics of the prior distribution at time $t-1$. Therefore, instead of setting $\prior(\Lat_1), ..., \prior(\Lat_T)$ to be independent unit gaussian distributions, the mean and variance of $\prior(\Lat_t)$ depends on the $\hdec_{t-1}$, which forms a Markov chain $\prior(\Lat_1), \prior(\Lat_2\given\Lat_1), ..., \prior(\Lat_T\given\Lat_{T-1})$ as in \citep{bachman_sdm}, where 
\begin{align}
\mu_{t}^{prior} &= tanh(W_{\mu}\hdec_{t-1})\\
\sigma_{t}^{prior} &= exp(tanh(W_{\sigma}\hdec_{t-1})) 
\end{align}
Overall, the loss function $\loss$ is calculated as follows:
\begin{align}
\loss =  &\expectation_{Q(\Lat_{1:t}\given\icaption,\oimage)}\left[ - \log p(\oimage\given\icaption,\Lat_{1:T}) + \sum_{t=2}^T\kldiv\left(\post(\Lat_t\given\Lat_{t-1},\icaption,\oimage)\klBars\prior(\Lat_t\given\Lat_{t-1},\icaption)\right) \right] \nonumber \\& + \kldiv\left(\post(\Lat_1\given\icaption,\oimage)\klBars\prior(\Lat_1\given\icaption)\right).
\end{align}
The expectation can be approximate by $\numSamples$ Monte Carlo samples $\LatSample_{1:T}$ from $\post(\Lat_{1:T}\given\icaption, \oimage)$:
\begin{align}
\loss \approx  &\frac{1}{\numSamples}\sum_{\sampleIdx=1}^\numSamples\left[ - \log p(\oimage\given\icaption,\LatSample^\sampleIdx_{1:T}) + \sum_{t=2}^T\kldiv\left(\post(\Lat_t\given\LatSample^\sampleIdx_{t-1},\icaption,\oimage)\klBars\prior(\Lat_t\given\LatSample^\sampleIdx_{t-1},\icaption)\right) \right] \nonumber \\& + \kldiv\left(\post(\Lat_1\given\icaption,\oimage)\klBars\prior(\Lat_1\given\icaption)\right).
\end{align}
\comm{
\begin{align}
\loss &= -\sum_{t=1}^{T}D_{KL}(\post(\Lat_t|\henc_t,s_{t-1})\,||\,\prior(\Lat_t)) + \frac{1}{L}\sum_{l=1}^{L}log\,p(x_{t}|y,z)\\
&=
\frac{1}{2}\sum_{t=1}^{T}(1 - 2\,log\,\sigma_{t}^{prior} + 2\,log\,\sigma_{t} - \frac{exp(2\,log\,\sigma_{t}) + (\mu_{t} - \mu_{t}^{prior})^{2}}{exp(2\,log\,\sigma_{t}^{prior})}) + \frac{1}{L}\sum_{l=1}^{L}log\,p(x_{t}|y,z)
\end{align}
}

\subsection{Generating Images from Captions}

@@

\vspace{-0.3cm}
\begin{figure}[h]
\captionsetup[subfigure]{labelformat=empty}
\begin{center}
\subfloat[A \underline{yellow} school bus parked in a parking lot.
]{\includegraphics[width=0.22\textwidth]{figures/a-yellow-school-bus-parked-in-a-parking-lot-sharp.png}}\quad
%
\subfloat[A \underline{red} school bus parked in a parking lot.
]{\includegraphics[width=0.22\textwidth]{figures/a-red-school-bus-parked-in-a-parking-lot-sharp.png}}\quad
%
\subfloat[A \underline{green} school bus parked in a parking lot.
]{\includegraphics[width=0.22\textwidth]{figures/a-green-school-bus-parked-in-a-parking-lot-sharp.png}}\quad
%
\subfloat[A \underline{blue} school bus parked in a parking lot.
]{\includegraphics[width=0.22\textwidth]{figures/a-blue-school-bus-parked-in-a-parking-lot-sharp.png}}\quad
%
\end{center}
%\caption{whole image caption}
\label{fig:label}
\vspace{-0.2cm}
\end{figure}

@@

\vspace{-0.3cm}
\begin{figure}[h]
\captionsetup[subfigure]{labelformat=empty}
\begin{center}
\subfloat[A very large commercial plane flying in the \underline{blue} skies.
]{\includegraphics[width=0.48\textwidth]{figures/a-very-large-commercial-plane-flying-in-the-blue-skies-sharp.png}}\quad
%
\subfloat[A very large commercial plane flying in the \underline{cloudy} skies.
]{\includegraphics[width=0.48\textwidth]{figures/a-very-large-commercial-plane-flying-in-the-cloudy-skies-sharp.png}}\quad
%
%
\end{center}
%\caption{whole image caption}
\label{fig:label}
\vspace{-0.8cm}
\end{figure}

\begin{figure}[h]
\captionsetup[subfigure]{labelformat=empty}
\begin{center}
\subfloat[A heard of elephants walking across a \underline{dry} grass field.
]{\includegraphics[width=0.48\textwidth]{figures/a-herd-of-elephants-walking-across-a-dry-grass-field-sharp.png}}\quad
%
\subfloat[A heard of elephants walking across a \underline{green} grass field.
]{\includegraphics[width=0.48\textwidth]{figures/a-herd-of-elephants-walking-across-a-green-grass-field-sharp.png}}\quad
%
%
\end{center}
%\caption{whole image caption}
\label{fig:label}
\vspace{-0.2cm}
\end{figure}

@@

\vspace{-0.3cm}
\begin{figure}[h]
\captionsetup[subfigure]{labelformat=empty}
\begin{center}
\subfloat[The \underline{decadent chocolate dessert} is on the table.
]{\includegraphics[width=0.48\textwidth]{figures/the-decadent-chocolate-dessert-is-on-the-table-2-sharp.png}}\quad
%
\subfloat[The \underline{bowl of banas} is on the table.
]{\includegraphics[width=0.48\textwidth]{figures/a-bowl-of-bananas-is-on-the-table-2-sharp.png}}\quad
%
%
\end{center}
%\caption{whole image caption}
\label{fig:label}
\vspace{-0.8cm}
\end{figure}

\begin{figure}[!h]
\captionsetup[subfigure]{labelformat=empty}
\begin{center}
\subfloat[A vintage photo of a \underline{cat}.
]{\includegraphics[width=0.48\textwidth]{figures/a-vintage-photo-of-a-cat-sharp.png}}\quad
%
\subfloat[A vintage photo of a \underline{dog}.
]{\includegraphics[width=0.48\textwidth]{figures/a-vintage-photo-of-a-dog-sharp.png}}\quad
%
%
\end{center}
%\caption{whole image caption}
\label{fig:labelr}
\vspace{-0.2cm}
\end{figure}

@@

To be added soon.

\subsubsection{Comparison With Other Models}
The quantitative evaluation of generative models has been a subject of ambiguity within a machine learning community. Compared to reporting classification accuracies, the measures defining generative models are intractable most of the times and might not correctly define the real quality of the model. To avoid ambiguity, we report results on two different metrics as well as do qualitative comparison of generative models.

As shown on Figure blah, we have sampled the images from the same caption in four of the best models.

First, to compare the the peformance of our model with other generative models trained with variational objective, we report the Recall$@$K, namely the mean number of sentences for which the correct image is ranked within the top-K retrieved results, based on the lower bound of likelihood $\loss$. If you want to get a really good results build a model like Ryan did. Do deal away with easy images we take ratio with ... with mean caption. To deal with large computational complexity of looping over each image we only consider closest neightbors. The precision Recall curve is reported there...

Second,

\vspace{-0.3cm}
\begin{figure}[!t]
\captionsetup[subfigure]{labelformat=empty}
\begin{center}
\subfloat{\includegraphics[width=0.22\textwidth]{figures/a-group-of-people-walk-on-a-beach-with-surf-boards-sharp.png}}\quad
%
\subfloat{\includegraphics[width=0.22\textwidth]{figures/a-group-of-people-walk-on-a-beach-with-surf-boards-lapgan.png}}\quad
%
\subfloat{\includegraphics[width=0.22\textwidth]{to-do.png}}\quad
%
\subfloat{\includegraphics[width=0.22\textwidth]{to-do.png}}\quad
%
\end{center}
\caption{Four different models displaying results from sampling caption \textit{A group of people walk on a beach with surf boards.}}
\label{fig:label}
\vspace{-0.2cm}
\end{figure}

\subsection{CIFAR}

>>>>

\documentclass{article} % For LaTeX2e
\usepackage{iclr-style/iclr2016_conference,times}
\usepackage{hyperref}
\usepackage{url}
\usepackage{amsmath}
\usepackage{graphicx}
\usepackage{caption}
%\usepackage{subcaption}
\usepackage{subfig}
\usepackage{tabulary}
\usepackage{soul}
\usepackage{color}
\usepackage{xcolor}
%\usepackage{floatrow}
% Table float box with bottom caption, box width adjusted to content
%\newfloatcommand{capbtabbox}{table}[][\FBwidth]

\newcommand{\sigmoid}{\boldsymbol{\sigma}}
\newcommand{\hlang}{h^{lang}}
\newcommand{\hlangall}{\boldsymbol{h^{lang}}}
\newcommand{\hdec}{h^{dec}}
\newcommand{\henc}{h^{enc}}
\newcommand{\readop}{\mathit{read}}
\newcommand{\writeop}{\mathit{write}}
\newcommand{\encoder}{\mathit{LSTM}^{enc}}
\newcommand{\decoder}{\mathit{LSTM}^{dec}}
\newcommand{\canv}{c}
\newcommand{\lat}{z}
\newcommand{\Lat}{Z}
\newcommand{\post}{Q}
\newcommand{\prior}{P}
\newcommand{\loss}{\mathcal{L}}
\newcommand{\lloss}{\mathcal{L}^{z}}
\newcommand{\rloss}{\mathcal{L}^{x}}
\newcommand{\hlc}[2][yellow]{{\sethlcolor{#1}\hl{#2}}}
\definecolor{0}{RGB}{247,251,255}
\definecolor{1}{RGB}{222,235,247}
\definecolor{2}{RGB}{198,219,239}
\definecolor{3}{RGB}{158,202,225}
\definecolor{4}{RGB}{107,174,214}
\definecolor{5}{RGB}{66,146,198}

@@

Generating realistic images from their descriptions is a very hard task that combines together two challenging problems of language modelling and image generation. Effectively, the model has to capture the semantic meaning expressed in the description and then use that knowledge to generate the pixel intensities of the image. Generating images from captions is a significantly harder problem than a reverse problem of generating captions from images which has recenly attracted a lot of attention from machine learning research community \citep{karpathy_captions}, \citep{xu_captions}, \citep{kiros_captions} and etc.

By using a sequence to sequence framework to approach the problem of image generation from captions, our model iteratively draws the patches on canvas, while attending to the relevant words in the description.

@@

\hlc[1]{Deep} \hlc[2]{Neural} \hlc[3]{Networks} \hlc[4]{have} \hlc[0]{achieved} a remarkable performance in various tasks such as image recognition \citep{krizhevsky_imagenet}, speech transcription \citep{graves_speech} and etc. While most of the recent success has been achieved by discriminative models, the generative models have not yet enjoyed the same level of success. Most of the previous work in generative models has been focused on variants of Boltzmann Machines \citep{smolensky_rbm}, \citep{russ_dbm} and Deep Belief Networks \citep{hinton_dbn}. While these models are very powerful, each iteration of training requires a computationally costly step of MCMC to approximate an intractable normalization constant that makes it hard to scale them to large datasets.

@@

\section{Model}

Our proposed model can be seen as a part of sequence-to-sequence framework \citep{ilya_mt}, \citep{cho_mt}, \citep{nitish_video} where captions are represented as a sequence of consecutive words and images are represented as a sequence of patches drawn on canvas over time $t=1,...,T$. Let $y$ be the input caption, consisting of $N$ words $y_{1}, y_{2}, ..., y_{n}$ and $x$ be the image corresponding to that caption.

\subsection{Encoder}

The encoder is a deterministic Bidirectional LSTM that encodes the variable size sentences into the vector representation $s$. Bidirectional LSTM consists of one Forward LSTM and Backward LSTM which combine information from past and future respectively. The Forward LSTM computes the sequence of forward hidden states $[\overrightarrow{h}^{lang}_{1}, \overrightarrow{h}^{lang}_{2}, ..., \overrightarrow{h}^{lang}_{N}]$ , whereas the Backward LSTM computes the sequence of backward hidden states $[\overleftarrow{h}^{lang}_{1}, \overleftarrow{h}^{lang}_{2}, ..., \overleftarrow{h}^{lang}_{N}]$. Then these hidden states are concatenated together into the sequence $[\hlang_{1}, \hlang_{2}, ..., \hlang_{N}]$, where $\hlang_{n} = [\overrightarrow{h}^{lang}_{n}, \overleftarrow{h}^{lang}_{n}], 1\leq n\leq N$.

The final representation of the sentence is calculated as follows:
\begin{align}
s_{t} = \alpha_{1}\hlang_{1} + \alpha_{2}\hlang_{2} + ... + \alpha_{N}\hlang_{N}
\end{align}
where $\hlang_{0}$ is initialized to the learned bias.
Setting $\alpha_{1...N}$ to $\frac{1}{N}$ turns the encoder into the vanilla model introduced in \citep{cho_mt} without the attention. We will describe how $\alpha_{1...N}$ are calculated in the next section.

\subsection{Decoder}

The decoder is a DRAW model, which is a stochastic recurrent neural network that consists of Inference LSTM that infers the distribution of latent variables of image $x$ given $y$ and then the Generator LSTM that uses the inferred latent variables in order to reconstruct the image $x$ given $y$. Formally, the decoder iteratively computes the following equations for $t=1,...,T$
\begin{align}
\label{eq:x_hat}
\hat{x}_t &= x-\sigmoid(\canv_{t-1})\\
\label{eq:read}
r_t &= \readop(x_t, \hat{x}_t, \hdec_{t-1})\\
\henc_t &= \encoder(\henc_{t-1}, [r_t, \hdec_{t-1}])\\
\lat_t &\sim \post(\Lat_t|\henc_t)\\
\hdec_t &= \decoder(\hdec_{t-1}, z_t, s_{t-1})\\
s_{t} &= align(\hdec_{t-1}, \hlangall)\\
\label{eq:write}
\canv_t &= \canv_{t-1} + \writeop(\hdec_t)
\end{align}

where $\readop$ and $\writeop$ are the same attention operators as in \citep{gregor_draw}, $\hlangall = [\hlang_{1}, \hlang_{2}, ..., \hlang_{n}]$ and $\canv_{0}, \hdec_{0}, \henc_{0}$ are initialized to the learned biases.

The $align$ function introduced by \cite{bahdanau_mt} is used to compute probabilities $\alpha_{1...n}$ by first computing the energies $e_{t,0}, e_{t,1}, ..., e_{t,n}$ and then rescaling them to the probability distribution $\alpha_{1}, \alpha_{2}, ..., \alpha_{n}$
\begin{align}
e_{tj} &= v^{T}tanh(U\hlang_{j} + W\hdec_{t} + b)\\
\alpha_{j} &= softmax(e_{tj})
\end{align}

where $softmax(e_{tj}) = \frac{exp(e_{tj})}{\sum_{j=1}^{N}exp(e_{tj})}$

@@

The latent loss is a negative sum of Kullback--Leibler divergence terms between distribution $\post(\Lat_t|\henc_t)$ and some prior distribution ${\prior(\Lat_t)}$ over time $t=1,...,T$, which can be seen as a regularization term. Since the patches drawn on canvas over time are not independent of each other, naturally the sufficient statistics of the prior distribution at time $t$ should be dependent on the sufficient statistics of the prior distribution at time $t-1$. Therefore, instead of setting $\prior(\Lat_1), ..., \prior(\Lat_T)$ to be independent unit gaussian distributions, the mean and variance of $\prior(\Lat_t)$ depends on the $\hdec_{t-1}$, as in \citep{bachman_sdm}, where 
\begin{align}
\mu_{t}^{prior} &= tanh(W_{mu}\hdec_{t-1})\\
\sigma_{t}^{prior} &= exp(tanh(W_{\sigma}\hdec_{t-1})) 
\end{align}
Overall, the likelihood $\loss$ is calculated as follows:
\begin{align}
\loss &= -\sum_{t=1}^{T}D_{KL}(\post(\Lat_t|\henc_t,s_{t-1})\,||\,\prior(\Lat_t)) + \frac{1}{L}\sum_{l=1}^{L}log\,p(x_{t}|y,z)\\
&=
\frac{1}{2}\sum_{t=1}^{T}(1 - 2\,log\,\sigma_{t}^{prior} + 2\,log\,\sigma_{t} - \frac{exp(2\,log\,\sigma_{t}) + (\mu_{t} - \mu_{t}^{prior})^{2}}{exp(2\,log\,\sigma_{t}^{prior})}) + \frac{1}{L}\sum_{l=1}^{L}log\,p(x_{t}|y,z)
\end{align}

\subsection{Image Generation}

@@

\vspace{-0.3cm}
\begin{figure}[h]
\captionsetup[subfigure]{labelformat=empty}
\begin{center}
\subfloat[A \underline{yellow} school bus parked in a parking lot.
]{\includegraphics[width=0.23\textwidth]{figures/new/a-yellow-school-bus-parked-in-a-parking-lot-sharp.png}}\quad
%
\subfloat[A \underline{red} school bus parked in a parking lot.
]{\includegraphics[width=0.23\textwidth]{figures/new/a-red-school-bus-parked-in-a-parking-lot-sharp.png}}\quad
%
\subfloat[A \underline{green} school bus parked in a parking lot.
]{\includegraphics[width=0.23\textwidth]{figures/new/a-green-school-bus-parked-in-a-parking-lot-sharp.png}}\quad
%
\subfloat[A \underline{blue} school bus parked in a parking lot.
]{\includegraphics[width=0.23\textwidth]{figures/new/a-blue-school-bus-parked-in-a-parking-lot-sharp.png}}\quad
%
\end{center}
%\caption{whole image caption}
\label{fig:label}
\vspace{-0.2cm}
\end{figure}

@@

\vspace{-0.3cm}
\begin{figure}[h]
\captionsetup[subfigure]{labelformat=empty}
\begin{center}
\subfloat[A very large commercial plane flying in \underline{blue} skies.
]{\includegraphics[width=0.23\textwidth]{figures/new/a-very-large-commercial-plane-flying-in-blue-skies-sharp.png}}\quad
%
\subfloat[A very large commercial plane flying in \underline{rainy} skies.
]{\includegraphics[width=0.23\textwidth]{figures/new/a-very-large-commercial-plane-flying-in-rainy-skies-sharp.png}}\quad
%
\subfloat[A herd of elephants walking across a \underline{dry} grass field.
]{\includegraphics[width=0.23\textwidth]{figures/new/a-herd-of-elephants-walking-across-a-dry-grass-field-sharp.png}}\quad
%
\subfloat[A herd of elephants walking across a \underline{green} grass field.
]{\includegraphics[width=0.23\textwidth]{figures/new/a-herd-of-elephants-walking-across-a-green-grass-field-sharp.png}}\quad
%
\end{center}
%\caption{whole image caption}
\label{fig:label}
\vspace{-0.2cm}
\end{figure}

\vspace{-0.5cm}
\caption{Closest images from the training set in the pixel space}
\begin{figure}[h]
\captionsetup[subfigure]{labelformat=empty}
\begin{center}
\subfloat[]{\includegraphics[width=0.23\textwidth]{figures/new/a-very-large-commercial-plane-flying-in-blue-skies-closest.png}}\quad
%
\subfloat[]{\includegraphics[width=0.23\textwidth]{figures/new/a-very-large-commercial-plane-flying-in-rainy-skies-closest.png}}\quad
%
\subfloat[]{\includegraphics[width=0.23\textwidth]{figures/new/a-herd-of-elephants-walking-across-a-dry-grass-field-closest.png}}\quad
%
\subfloat[]{\includegraphics[width=0.23\textwidth]{figures/new/a-herd-of-elephants-walking-across-a-green-grass-field-closest.png}}\quad
%
\end{center}
\label{fig:label}
\vspace{-0.5cm}
\end{figure}

%\vspace{-0.3cm}
%\begin{figure}[h]
%\captionsetup[subfigure]{labelformat=empty}
%\begin{center}
%\subfloat[A very large commercial plane flying in the \underline{blue} skies.
%]{\includegraphics[width=0.48\textwidth]{figures/a-very-large-commercial-plane-flying-in-the-blue-skies-sharp.png}}\quad
%
%\subfloat[A very large commercial plane flying in the \underline{cloudy} skies.
%]{\includegraphics[width=0.48\textwidth]{figures/a-very-large-commercial-plane-flying-in-the-cloudy-skies-sharp.png}}\quad
%
%
%\end{center}
%\caption{whole image caption}
%\label{fig:label}
%\vspace{-0.8cm}
%\end{figure}

%\begin{figure}[h]
%\captionsetup[subfigure]{labelformat=empty}
%\begin{center}
%\subfloat[A herd of elephants walking across a \underline{dry} grass field.
%]{\includegraphics[width=0.48\textwidth]{figures/a-herd-of-elephants-walking-across-a-dry-grass-field-sharp.png}}\quad
%
%\subfloat[A herd of elephants walking across a \underline{green} grass field.
%]{\includegraphics[width=0.48\textwidth]{figures/a-herd-of-elephants-walking-across-a-green-grass-field-sharp.png}}\quad
%
%
%\end{center}
%\caption{whole image caption}
%\label{fig:label}
%\vspace{-0.2cm}
%\end{figure}

@@

\vspace{-0.3cm}
\begin{figure}[h]
\captionsetup[subfigure]{labelformat=empty}
\begin{center}
\subfloat[\underline{The decadent chocolate} \underline{desert} is on the table.
]{\includegraphics[width=0.23\textwidth]{figures/new/the-decadent-chocolate-dessert-is-on-the-table-sharp.png}}\quad
%
\subfloat[\underline{A bowl of banas} is on the table.
]{\includegraphics[width=0.23\textwidth]{figures/new/a-bowl-of-bananas-is-on-the-table-sharp.png}}\quad
%
\subfloat[A vintage photo of a \underline{cat}.
]{\includegraphics[width=0.23\textwidth]{figures/new/a-vintage-photo-of-a-cat-sharp.png}}\quad
%
\subfloat[A vintage photo of a \underline{dog}.
]{\includegraphics[width=0.23\textwidth]{figures/new/a-vintage-photo-of-a-dog-sharp.png}}\quad
%
\end{center}
%\caption{whole image caption}
\label{fig:label}
\vspace{-0.2cm}
\end{figure}

%\vspace{-0.3cm}
%\begin{figure}[h]
%\captionsetup[subfigure]{labelformat=empty}
%\begin{center}
%\subfloat[\underline{The decadent chocolate dessert} is on the table.
%]{\includegraphics[width=0.48\textwidth]{figures/the-decadent-chocolate-dessert-is-on-the-table-2-sharp.png}}\quad
%
%\subfloat[\underline{A bowl of banas} is on the table.
%]{\includegraphics[width=0.48\textwidth]{figures/a-bowl-of-bananas-is-on-the-table-2-sharp.png}}\quad
%
%
%\end{center}
%\caption{whole image caption}
%\label{fig:label}
%\vspace{-0.8cm}
%\end{figure}

%\begin{figure}[!h]
%\captionsetup[subfigure]{labelformat=empty}
%\begin{center}
%\subfloat[A vintage photo of a \underline{cat}.
%]{\includegraphics[width=0.48\textwidth]{figures/a-vintage-photo-of-a-cat-sharp.png}}\quad
%
%\subfloat[A vintage photo of a \underline{dog}.
%]{\includegraphics[width=0.48\textwidth]{figures/a-vintage-photo-of-a-dog-sharp.png}}\quad
%
%
%\end{center}
%\caption{whole image caption}
%\label{fig:labelr}
%\vspace{-0.2cm}
%\end{figure}

@@

\subsubsection{Comparison With Other Models}
The quantitative evaluation of generative models has been a subject of ambiguity in a machine learning community. Compared to reporting classification accuracies in discriminative models, the measures defining generative models are intractable most of the times and might not correctly define the real quality of the model. To get a better comparisions between performances of generative models, we report results on two different metrics as well as do some qualitative comparison of different generative models.

As you can see on Figure~\ref{fig:diffmodels}, we generated several samples using each of the current state-of-the-art generative models corresponding to the caption \textit{A group of people walk on a beach with surf boards.}. The samples generated by variational models were sharpened by Adversarial Network trained on edge residuals as explained in ... While all of the samples look sharp, the images generated by LAPGAN look more noisy and have a less clear structure in them, whereas the images generated by variational models trained with L2 cost function have a watercolor effect on them.

As for the quantitative comparison of different models we first compare the performance of our model with other generative models trained with variational objective. We rank the images conditioned on some caption in the test set based on the variational lower bound of likelihood and then report the Precision-Recall metric to evaluate the quality of the generative model. As expected, the quality of image retrieval using generative models is worse compared to the models that were specifically build to do retrieval, like \cite{kiros_captions} which map captions and images to the same space. To deal with large computational complexity of looping through each image in the test set, we create a shortlist of 99 neighbors based on the convolutional features trained on CIFAR dataset. We found that the reconstruction error $\rloss$ increased for the sharpened version of generated images. Since the sharpening changes the color of image as well adds edges to it, computing reconstruction error for each pixel is not necessarily a good measure.

Instead of calculating reconstruction error for each pixel separately, we also evaluate all models by reporting Structural Similarity Index (SSI) which incoporates perceptual phenomena, such as luminace and contrast masking into the error calculation. By also considering that the pixels have strong inter-dependencies when they are close to each other, the metric is calculated on the small windows of the image. We sampled 50 images from prior per each test caption for each generative model and calculated SSI between real image and the generated images. The SSI results are reported in Table~\ref{tab:ssi}
